Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-11-23 automatica/paper.tex
results

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\
2  & Antenna  & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
4  & Bioreact & 3 & 16,8 & 11.2\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
5  & Chen\_ex1& 3 & 16,8 & 7.2\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
6  & Chen\_ex2 & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
7  & Chen\_ex3 & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
8  & Chen\_ex4 & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
9  & Cruise    & 1 & 16,8 & 6.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s (56.6\,s)\\
17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s (\xmark)\\
20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s (\xmark)\\
21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (2.4\,s)\\
22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s (313.6\,s)\\
26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s (6.0\,s)\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
4  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
5  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
6  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
9  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
10 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
13 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s (56.6\,s)\\
17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s (\xmark)\\
20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s (\xmark)\\
21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (2.4\,s)\\
22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s (313.6\,s)\\
26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s (6.0\,s)\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
